An Algorithm for Searching Evolving Graphs in Linear Algebraic Language

### 2016-01-22 paper.tex
update conclusion

In this paper, we have introduced and analyzed the evolving-graph BFS in both
graph and algebraic notation.
This paper leaves important extensions open for further research. First, it is
of interest to extend the evolving-graph BFS algorithm for weighted evolving graphs, which can provide more valuable information when the degree of connectivity is available in the data.
Second, efficient algebraic representations and algorithms need to be addressed.
One major advantage of representing evolving graphs as sparse matrices
is the matrix representation is highly structured so it is easy to design
high performance parallel implementations.
Third, depth-first search and other graph traversal algorithms can be
extended for searching evolving graphs using similar ideas.

>>>>

In this paper, we have introduced and analyzed the evolving-graph BFS in both
graph and algebraic notation. The relationship between active nodes and 
evolving graph algorithms is discussed.
This paper leaves important extensions open for further research. First, it is
of interest to extend the evolving-graph BFS algorithm for weighted evolving graphs, which can provide more valuable information when the degree of connectivity is available in the data.
Second, efficient algebraic representations and algorithms need to be addressed.
One major advantage of representing evolving graphs as sparse matrices
is the matrix representation is highly structured so it is easy to design
high performance parallel implementation.
Third, depth-first search and other graph traversal algorithms can be
extended using similar ideas.
